---
title: "What Makes a Good Wine?"
subtitle: "A Statistical Analysis of the Best Way to Select Wine"
author: "Hamilton Murrah, Kellyn McDonald, Naima Turbes"
output: pdf_document
---
```{r packages-data, warning=FALSE, message=FALSE, echo = FALSE}
library(tidyverse)
library(tidytext)
wine_data <- read_csv("data/winemag-data_first150k.csv") 
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
```
### Abstract

Several studies have tried to identify the "best wine" with differing results. This research study aims to characterize the relationship between a wine’s quality rating and its country of origin, price, variety, and words used in its description. We want to use this information to guide advice on selecting the best wines. We used a dataset of wine as rated by experts, and found higher ratings were associated with higher price and with being from Germany or Austria. We additionally found that red wines and those using “cherry” as a descriptor generally had higher scores regardless of price, but text analysis also suggested that in general, all wines used similar descriptors. We concluded that generally more expensive wines are perceived as better, but other variables also influence a wine's ranking. For example, extremely expensive or cheap wines might deviate from this trend. In these cases, generally red and cherry wines have higher scores regardless of price.

\newpage



### Introduction



People have cultivated and appreciated wine for millennia, with the oldest known winery dating to 4,100 B.C. Since then, wine production and consumption spread has become an important part of many cultures. Today, wine is often used as a celebratory drink during weddings or holidays, with fine wine being expensive and associated with higher social class[1].

Most current wine production happens in Europe. In 2019, Italy produced 21.6 million hectoliters of wine and was the world's largest wine producer. The next two largest wine producers that year were Spain and France, producing 21.3 million hectoliters and 14.2 million hectoliters respectively [2]. Nevertheless, a 2019 survey from Forbes found that the the best ranked wine was from Napa Valley in the United States [3]. We are curious to see if this has changed.

Our main motivation for investigating wine data is pure interest and desire to understand how to select the best wine. We are specifically interested in how the perceived quality of these wines varies based on where they were produced. Additionally, we want to understand what words wine sommeliers use to describe highly rated wines versus lower rated wines. Finally, in an attempt to find the best wine to buy, we want to investigate and characterize what wines have the best value for their rating. We hypothesize that the best wines are also the most expensive wines, come from France and Italy, and are described using positive descriptors.

### Methodology


We obtained a dataset from user zackthoutt on Kaggle, who scraped 150,929 observations from WineEnthusiast.com. Our primary outcome of interest was a numerical score from 1-100 given by WineEnthusiast, and we examined relationships with each wine’s country of origin, price, grape variety, and a text description from a sommelier.


We performed the following analyses in order to explore potential relationships:

1.	A linear model that predicted score based on country, grape variety, and price.
2.	Exploratory text analysis and visualization regarding key descriptors


### Results
 
``` {r highest_average_score_by_country, echo = FALSE, warning = F, message = F}
country_counts <- wine_data %>%
    group_by(country) %>%
    count(country) %>%
    filter(n >= 100)

relevant_countries <- wine_data %>%
    filter(!is.na(points) & !is.na(price)) %>%
    filter(country %in% country_counts$country)

best_country <- relevant_countries %>%
    filter(!is.na(country)) %>%
    select(country, points, price) %>%
    group_by(country) %>%
    summarize(avg = mean(points)) %>%
    arrange(desc(avg))


median_country <- median(relevant_countries$points)
mean_country <- mean(relevant_countries$points)

score_test <- wine_data %>%
    filter(!is.na(country)) %>%
    group_by(country) %>%
    summarize(avg = mean(points))

weighted_avg_test <- wine_data %>%
    group_by(country) %>%
    mutate(weighted_count = (points/price))
```

We performed basic exploratory analyses to get a feel for our data. When filtering only for countries with 100 or more wines present, the ratings generally fell in a narrow range (median 89, mean 88.86), with Austria having the highest average rating of 90.79 and Argentina having the lowest average rating of 86.51. Contrary to our hypothesis, Italy and France were not the top two countries. The top 5 countries with the highest average wine score are Austria, Germany, France, US, and Italy in that order. 

```{r highest_average_points_by_variety, warning = F, message = F, echo= FALSE}
variety_means <- wine_data %>% 
    group_by(variety) %>% 
    summarize(mean = mean(points)) %>% 
    arrange(desc(mean)) %>% 
    top_n(5)


variety_counts <- wine_data %>%
    group_by(variety) %>%
    count(variety) %>%
    filter(n >= 50)

variety_means_more_than_50 <- wine_data %>%
    group_by(variety) %>% 
    summarize(mean = mean(points)) %>% 
    arrange(desc(mean)) %>% 
    filter(variety %in% variety_counts$variety) %>%
    top_n(5)

```

We calculated the top 5 best rated varieties of wine similarly. After filtering only for varieties that have 50 or more wines present, the top 5 varieties presented in this calculation were Gewürztraminer, Grüner Veltliner, Pinot Gris, Pinot Noir, and Riesling. 

``` {r lowest_average_points_by_variety, message = F, warning = F, echo = F}
variety_means_more_than_50_bottom_5 <- wine_data %>%
    group_by(variety) %>% 
    summarize(mean = mean(points)) %>% 
    arrange((mean)) %>% 
    filter(variety %in% variety_counts$variety) %>%
    top_n(-5)
```

We again filtered the data to only consider varieties with 50 or more samples in the data set but this time found the bottom 5 varieties. The bottom 5 varieties were Portuguese White, Merlot, Malbec, White Blend, and Viognier.

The density plots of the point distribution for the top five countries are consistent with the mean point values calculated earlier. Austria has a very high density of wine scores around 90 that likely contributes to the country's higher average wine point score. 

The density plots for the point values for the top five varieties of wine display an interesting trend. Gewürztraminer, Pinot Gris, Pinot Noir, and Riesling varieties show more evenly distributed point values for wines whereas Grüner Veltliner's data distribution is concentrated around the 90 point value. Unlike with Austria, however, this larger density of wines around the 90 point value did not make the Grüner Veltliner the variety with the best average point value.

The density plots for the top five varieties and top five countries all look generally similar. The data is left skewed and most of the wines are less than 100 dollars. One noticeable difference is that the Gruner Veltliner variety and Austria have cheaper wines compared to the other top varieties or countries.

```{r points_countries_density, message = F, warning = F, echo = F, eval = F}
country_counts <- wine_data %>%
    group_by(country) %>%
    count(country) %>%
    filter(n >= 100)

top_countries <- wine_data %>% 
  filter(country == "Austria" |
           country == "Germany" |
           country == "France" |
           country == "US" |
           country == "Italy")

ggplot(data = top_countries, mapping = aes(points)) + 
  geom_density() + 
  facet_wrap(~country) +
  labs(x = "Points", y = "Density", title = "Austria has the highest density of wines that scored 90 or above")
```

```{r points_variety_density, message = F, warning = F, echo = F, eval = F}

top_var <- wine_data %>% 
  filter(variety == "Gewürztraminer" |
           variety == "Grüner Veltliner" |
           variety == "Pinot Gris" |
           variety == "Pinot Noir" |
           variety == "Riesling")

ggplot(data = top_var, mapping = aes(points)) + 
  geom_density() + 
  facet_wrap(~variety) +
  labs(x = "Points", y = "Density", title = "Grüner Veltiner has a concentrated density between 85 and 90 points")

```

The density plots for the point values for the top 5 varieties of wine display an interesting trend. Gewürztraminer, Pinot Gris, Pinot Noir, and Riesling varieties show more evenly distributed point values for wines whereas Grüner Veltliner's data distribution is concentrated around the 90 point value. Unlike with Austria, however, this larger density of wines around the 90 point value did not make the Grüner Veltliner the variety with the best average point value.

```{r price_countries_density, message = F, warning = F, echo = F, eval = F}

top_countries <- wine_data %>% 
  filter(country == "Austria" |
           country == "Germany" |
           country == "France" |
           country == "US" |
           country == "Italy")

ggplot(data = top_countries, mapping = aes(price)) + 
  geom_density() + 
  facet_wrap(~country) +
  labs(x = "Price", y = "Density", title = "The majority of wines in all top countries are cheap")

```

```{r price_variety_desnsity, message = F, warning = F, echo = F, eval = F}

top_var <- wine_data %>% 
  filter(variety == "Gewürztraminer" |
           variety == "Grüner Veltliner" |
           variety == "Pinot Gris" |
           variety == "Pinot Noir" |
           variety == "Riesling")

ggplot(data = top_var, mapping = aes(price)) + 
  geom_density() + 
  facet_wrap(~variety)+
  labs(x = "Price(USD)", y = "Density", title = "The majority of wines in all top varieties are cheap")

```

Overall, the density plots for the top five varieties and top five countries all look generally similar. The data is right skewed and most of the wines are less than 100 dollars. One noticeable difference is that both Austria and the Gruner Veltliner variety generally have cheaper wines compared to the other top varieties or countries.

```{r lm_tests, message = F, warning = F, echo = F}

lmthingy <- wine_data %>%
  mutate (top_countries = ifelse(country == "Austria" | country == "France"| country == "US" | country == "Italy" | country == "Germany", 1, 0)) %>%
  mutate (top_varieties = ifelse(variety == "Gewürztraminer" | variety == "Grüner Veltliner"| variety == "Pinot Gris" | variety == "Pinot Noir" | variety == "Riesling", 1, 0))

top_5_countries_and_other <- wine_data %>%
  mutate(top_countries = if_else(
    country == "Austria" |
    country == "France" |
    country == "US" |
    country == "Italy" |
    country == "Germany", country, "other"
)) %>%
  mutate(top_varieties = if_else(
    variety == "Gewürztraminer" |
    variety == "Grüner Veltliner" |
    variety == "Pinot Gris" |
    variety == "Pinot Noir" |
    variety == "Riesling", variety, "other"))

modell <- lm(points ~ price + top_countries + top_varieties, data = top_5_countries_and_other)

m_int_aug <- augment(modell)
```

predicted points = 91.80 + 0.03(price) - 2.16(France) - 2.97(Germany) - 2.44(Italy) - 2.43(US) - 2.71(other_country) - 1.67(Grüner_Veltliner) - 0.50(Pinot_Gris) - 0.95(Pinot_Noir) - 0.43(Riesling) - -1.84(other_variety)

This is a linear model that shows the predicted number of points for a particular wine when considering which country it is from (one of the top 5 or not), which variety it is (one of the top 5 or not), and its price (see **Appendix A** for this model). In this case our baseline variable is when the wine is from Austria and is a Gewürztraminer variety. So the predicted point value of a Gewürztraminer wine from Austria assuming all other variables are 0 is 91.8. We see that all of our values are negative for our variables excluding price. This is interesting, yet not surprising when we consider that Austria and Gewürztraminer are being used as our baseline and that they are also the country and the variety with the highest mean wine scores. So inherently every other country and variety must be lower than the baseline Curiously, the estimate decreases do not follow the order of their mean scores. For example, we know that Germany has the second highest mean score, but has the highest decrease in its estimate even when compared to countries outside of the top 5. This could be caused by the fact that Germany has a high mean score, but also a high variability in its scores compared to a country like Austria with a high density of scores around its mean. Also, Riesling is the 5th highest variety in terms of mean scores, and yet has the lowest estimated decrease when compared to all other varieties. This could be because many high scoring wines from Austria are of the Riesling variety.


``` {r sentiment_analysis_top_5_varieties, message = F, warning = F, echo = FALSE}
Gewürztraminer <- wine_data %>%
    filter(variety == "Gewürztraminer")
descriptions <- tibble(txt = Gewürztraminer$description)
unnested_Gewürztraminer <- descriptions %>%
  unnest_tokens(word, txt) %>%
    filter(word != "wine" & word != "flavors" & word != "palate" &
               word != "drink" & word != "aromas" & word != "offers" &
               word != "finish" & word != "notes" & word != "long" &
               word != "pinot" & word != "gris" & word != "generous" &
               word != "hints" & word != "gewürztraminer" & word != "noir" &
               word != "riesling" & word != "grüner" & word != "veltliner" &
               word != "nose" & word != "fresh" & word != "fruit") %>%
  anti_join(get_stopwords(source = "smart"))
Grüner_Veltliner <- wine_data %>%
    filter(variety == "Grüner Veltliner")
descriptions <- tibble(txt = Grüner_Veltliner$description)
unnested_Grüner_Veltliner <- descriptions %>%
  unnest_tokens(word, txt) %>%
    filter(word != "wine" & word != "flavors" & word != "palate" &
               word != "drink" & word != "aromas" & word != "offers" &
               word != "finish" & word != "notes" & word != "long" &
               word != "pinot" & word != "gris" & word != "generous" &
               word != "hints" & word != "gewürztraminer" & word != "noir" &
               word != "riesling" & word != "grüner" & word != "veltliner" &
               word != "nose" & word != "fresh" & word != "fruit") %>%
  anti_join(get_stopwords(source = "smart"))
Pinot_Gris <- wine_data %>%
    filter(variety == "Pinot Gris")
descriptions <- tibble(txt = Pinot_Gris$description)
unnested_Pinot_Gris <- descriptions %>%
  unnest_tokens(word, txt) %>%
    filter(word != "wine" & word != "flavors" & word != "palate" &
               word != "drink" & word != "aromas" & word != "offers" &
               word != "finish" & word != "notes" & word != "long" &
               word != "pinot" & word != "gris" & word != "generous" &
               word != "hints" & word != "gewürztraminer" & word != "noir" &
               word != "riesling" & word != "grüner" & word != "veltliner" &
               word != "nose" & word != "fresh" & word != "fruit") %>%
  anti_join(get_stopwords(source = "smart"))
Pinot_Noir <- wine_data %>%
    filter(variety == "Pinot Noir")
descriptions <- tibble(txt = Pinot_Noir$description)
unnested_Pinot_Noir <- descriptions %>%
  unnest_tokens(word, txt) %>%
    filter(word != "wine" & word != "flavors" & word != "palate" &
               word != "drink" & word != "aromas" & word != "offers" &
               word != "finish" & word != "notes" & word != "long" &
               word != "pinot" & word != "gris" & word != "generous" &
               word != "hints" & word != "gewürztraminer" & word != "noir" &
               word != "riesling" & word != "grüner" & word != "veltliner" &
               word != "nose" & word != "fresh" & word != "fruit") %>%
  anti_join(get_stopwords(source = "smart"))
Riesling <- wine_data %>%
    filter(variety == "Riesling")
descriptions <- tibble(txt = Riesling$description)
unnested_Riesling <- descriptions %>%
  unnest_tokens(word, txt) %>%
    filter(word != "wine" & word != "flavors" & word != "palate" &
               word != "drink" & word != "aromas" & word != "offers" &
               word != "finish" & word != "notes" & word != "long" &
               word != "pinot" & word != "gris" & word != "generous" &
               word != "hints" & word != "gewürztraminer" & word != "noir" &
               word != "riesling" & word != "grüner" & word != "veltliner" &
               word != "nose" & word != "fresh" & word != "fruit") %>%
  anti_join(get_stopwords(source = "smart"))
```
``` {r sentiment_analysis_bottom_5_varieties, message = F, warning = F, echo = F}
Portuguese_White <- wine_data %>%
    filter(variety == "Portuguese White")
descriptions <- tibble(txt = Portuguese_White$description)
unnested_Portuguese_White <- descriptions %>%
  unnest_tokens(word, txt) %>%
    filter(word != "wine" & word != "flavors" & word != "palate" &
               word != "drink" & word != "aromas" & word != "offers" &
               word != "finish" & word != "notes" & word != "long" &
               word != "generous" & word != "hints" & word != "nose" &
               word != "fresh" & word != "fruit" & word != "full" & 
               word != "character" & word != "ready" & word != "100" & 
               word != "merlot" & word != "texture" & word != "end" & 
               word != "medium" & word != "bodied" & word != "malbec" & 
               word != "portuguese" & word != "chardonnay" & word != "blanc" &
               word != "viognier" & word != "note" & word != "show" &
               word != "vineyard" & word != "style" & word != "shows" & 
               word != "make" & word != "pinot" & word != "sauvignon" &
               word != "body" & word != "bottling" & word != "alongside") %>%
  anti_join(get_stopwords(source = "smart"))
Merlot <- wine_data %>%
    filter(variety == "Merlot")
descriptions <- tibble(txt = Merlot$description)
unnested_Merlot <- descriptions %>%
  unnest_tokens(word, txt) %>%
    filter(word != "wine" & word != "flavors" & word != "palate" &
               word != "drink" & word != "aromas" & word != "offers" &
               word != "finish" & word != "notes" & word != "long" &
               word != "generous" & word != "hints" & word != "nose" &
               word != "fresh" & word != "fruit" & word != "full" & 
               word != "character" & word != "ready" & word != "100" & 
               word != "merlot" & word != "texture" & word != "end" & 
               word != "medium" & word != "bodied" & word != "malbec" & 
               word != "portuguese" & word != "chardonnay" & word != "blanc" &
               word != "viognier" & word != "note" & word != "show" &
               word != "vineyard" & word != "style" & word != "shows" & 
               word != "make" & word != "pinot" & word != "sauvignon" &
               word != "body" & word != "bottling" & word != "alongside") %>%
  anti_join(get_stopwords(source = "smart"))
Malbec <- wine_data %>%
    filter(variety == "Malbec")
descriptions <- tibble(txt = Malbec$description)
unnested_Malbec <- descriptions %>%
  unnest_tokens(word, txt) %>%
    filter(word != "wine" & word != "flavors" & word != "palate" &
               word != "drink" & word != "aromas" & word != "offers" &
               word != "finish" & word != "notes" & word != "long" &
               word != "generous" & word != "hints" & word != "nose" &
               word != "fresh" & word != "fruit" & word != "full" & 
               word != "character" & word != "ready" & word != "100" & 
               word != "merlot" & word != "texture" & word != "end" & 
               word != "medium" & word != "bodied" & word != "malbec" & 
               word != "portuguese" & word != "chardonnay" & word != "blanc" &
               word != "viognier" & word != "note" & word != "show" &
               word != "vineyard" & word != "style" & word != "shows" & 
               word != "make" & word != "pinot" & word != "sauvignon" &
               word != "body" & word != "bottling" & word != "alongside") %>%
  anti_join(get_stopwords(source = "smart"))
White_Blend <- wine_data %>%
    filter(variety == "White Blend")
descriptions <- tibble(txt = White_Blend$description)
unnested_White_Blend <- descriptions %>%
  unnest_tokens(word, txt) %>%
    filter(word != "wine" & word != "flavors" & word != "palate" &
               word != "drink" & word != "aromas" & word != "offers" &
               word != "finish" & word != "notes" & word != "long" &
               word != "generous" & word != "hints" & word != "nose" &
               word != "fresh" & word != "fruit" & word != "full" & 
               word != "character" & word != "ready" & word != "100" & 
               word != "merlot" & word != "texture" & word != "end" & 
               word != "medium" & word != "bodied" & word != "malbec" & 
               word != "portuguese" & word != "chardonnay" & word != "blanc" &
               word != "viognier" & word != "note" & word != "show" &
               word != "vineyard" & word != "style" & word != "shows" & 
               word != "make" & word != "pinot" & word != "sauvignon" &
               word != "body" & word != "bottling" & word != "alongside") %>%
  anti_join(get_stopwords(source = "smart"))
Viognier <- wine_data %>%
    filter(variety == "Viognier")
descriptions <- tibble(txt = Viognier$description)
unnested_Viognier <- descriptions %>%
  unnest_tokens(word, txt) %>%
    filter(word != "wine" & word != "flavors" & word != "palate" &
               word != "drink" & word != "aromas" & word != "offers" &
               word != "finish" & word != "notes" & word != "long" &
               word != "generous" & word != "hints" & word != "nose" &
               word != "fresh" & word != "fruit" & word != "full" & 
               word != "character" & word != "ready" & word != "100" & 
               word != "merlot" & word != "texture" & word != "end" & 
               word != "medium" & word != "bodied" & word != "malbec" & 
               word != "portuguese" & word != "chardonnay" & word != "blanc" &
               word != "viognier" & word != "note" & word != "show" &
               word != "vineyard" & word != "style" & word != "shows" & 
               word != "make" & word != "pinot" & word != "sauvignon" &
               word != "body" & word != "bottling" & word != "alongside") %>%
  anti_join(get_stopwords(source = "smart"))
```
``` {r descriptor_word_differences, message = F, warning = F, echo = F}
top_5_descriptors <- tibble(word = union_all(unnested_Gewürztraminer$word, 
               unnested_Grüner_Veltliner$word,
               unnested_Pinot_Gris$word,
               unnested_Pinot_Noir$word,
               unnested_Riesling$word))
top_5_descriptor_counts <- top_5_descriptors %>%
  count(word) %>%
  mutate(prob = round(n/sum(n),4)) %>%
  arrange(desc(prob)) %>%
  top_n(10)
bottom_5_descriptors <- tibble(word = union_all(unnested_Portuguese_White$word,
               unnested_White_Blend$word,
               unnested_Malbec$word,
               unnested_Merlot$word,
               unnested_Viognier$word))
bottom_5_descriptor_counts <- bottom_5_descriptors %>%
  count(word) %>%
  mutate(prob = round(n/sum(n),4)) %>%
  arrange(desc(prob)) %>%
  top_n(10)
```

There are a surprising amount of similarities in the most commonly used descriptor words for the top and bottom 5 wine varieties (see **Appendix B** and **Appendix C** for these visualizations). We see that tannins and lemon both fall near the bottom of the graph for both groups, but that the words acidity and ripe fall in the top 4 for both graphs as well. On the other hand, we see some differences in the data. For example, we see that the word cherry is very commonly used in the descriptions of the top 5 wines (nearly 1.5% of all words used was the cherry!). We also see dry and red rounding out the top 5.

``` {r sentiment_analysis_expensive_and_cheap, warning = F, message = F, echo = FALSE}
over_200 <- wine_data %>%
    filter(price >= 200)
descriptions <- tibble(txt = over_200$description)
unnested_over_200 <- descriptions %>%
  unnest_tokens(word, txt) %>%
    filter(word != "wine" & word != "flavors" & word != "palate" &
               word != "drink" & word != "aromas" & word != "offers" &
               word != "finish" & word != "notes" & word != "long" &
               word != "alongside" & word != "dense" & word != "full" & 
               word != "dried" & word != "nose" & word != "shows" &
               word != "bodied" & word != "fruit" & word != "concentrated" &
               word != "years" & word != "vineyard" & word != "structure" &
               word != "age" & word != "fruits") %>%
    anti_join(get_stopwords(source = "smart"))
under_10 <- wine_data %>%
    filter(price <= 10)
descriptions <- tibble(txt = under_10$description)
unnested_under_10 <- descriptions %>%
  unnest_tokens(word, txt) %>%
    filter(word != "wine" & word != "flavors" & word != "palate" &
               word != "drink" & word != "aromas" & word != "offers" &
               word != "finish" & word != "notes" & word != "long" &
               word != "alongside" & word != "dense" & word != "full" & 
               word != "dried" & word != "nose" & word != "shows" &
               word != "bodied" & word != "fruit" & word != "concentrated" &
               word != "years" & word != "vineyard" & word != "structure" &
               word != "age" & word != "fruits") %>%
    anti_join(get_stopwords(source = "smart"))
```
``` {r expensive_vs_cheap_wines_text_analysis, warning = F, message = F, echo = F}
expensive_wine_word_counts <- unnested_over_200 %>%
  count(word) %>%
  mutate(prob = round(n/sum(n),4)) %>%
  arrange(desc(prob)) %>%
  top_n(10)
cheap_wine_word_counts <- unnested_under_10 %>%
  count(word) %>%
  mutate(prob = round(n/sum(n),4)) %>%
  arrange(desc(prob)) %>%
  top_n(10)
```
Here we are separating the wines by expensive (>= $200) and cheap (<= $10). Again, we see some immediate similarities between the two. For example, we see tannins, red, black, ripe, and berry falling at different positions for each throughout the graph (see **Appendix D** and **Appendix E** for these visualizations). There don't seem to be any similarities as to where they appear in the lists (i.e. appears in the top 3 for both), but it is interesting to note that they are present in both. Acidity makes sense as to why it appears as it is present in all wines, although it is interesting that it is the most common descriptor for cheaper wines by a fair margin. Another thing to note is that both categories have the word red fairly often (presumably referencing red wine) and we know from our top wine varieties that red wine tends to be rated more highly. We expected the cheap wines to reference white more often, however this was not the case. On the expensive side, we see the words oak, aging, and berry. Perhaps it is the case that these expensive wines are more likely to be stored and aged in higher quality barrels (oak may be the preferred substance) than cheaper ones. The presence of aging makes sense since there tends to be a correlation between older wines and higher prices. Berry is intriguing though. Recall that berry was one of the descriptors present in the bottom 5 wines from above. We find it very interesting that there is this correlation between expensive wines and lowly rated wines. Additionally, both black and ripe appear in the same places in the expensive chart as they do in the bottom 5 wine chart. While both of these words are also present in the cheaper wine charts, this is expected as we hypothesized that cheaper wines would correlate higher with lower rated wines. This leads us to the conclusion that more expensive wines do not necessarily imply higher scoring wines. There may even be correlations to the contrary. Similarly, we see that cherry is 10th most commonly occurring word for the cheap wines and it is also the most commonly occurring word for the top 5 wines. This is a very interesting correlation and, when paired with our observations from the previous paragraph, make us begin to question whether paying more for wine is really worth it overall. There are certainly outliers on both sides, but it seems that there tends to be a correlation between cheap wine and highly rated wine, as well as one between expensive wine and lowly rated wine.

``` {r weighted_wine_scores_to_price, message = FALSE, warning = FALSE, echo = FALSE, eval = F}
weighted_avg <- wine_data %>%
    group_by(country)%>%
    summarize(country, winery, variety, price, country, points, weighted = points/price) %>%
        arrange(desc(weighted))
weighted_avg <- relevant_countries %>% 
    mutate(weighted = log((price/points), base = exp(1))) %>% 
    mutate(top_3 = if_else(country == "Austria" |
                               country == "Germany" |
                               country == "France",
                           country, "Other"))
ggplot(data = weighted_avg, mapping = aes(x = price, y = weighted)) + 
    geom_point() + 
    geom_smooth(method = "lm", se = F) + facet_wrap(~top_3) +  labs(title = "Positive Relationship Between Weighted Points Value and Price",
         y = "Log(Price/Points)",
         x = "Price")
```

```{r austria_vis, message = F, warning = F, echo = F, eval = F}
austria <- relevant_countries %>% 
    mutate(weighted = log((price/points), base = exp(1))) %>% 
    filter (country == "Austria")
ggplot(data = austria, mapping = aes(x = price, y = weighted)) + 
    geom_point() + 
    geom_smooth(method = "lm", se = F) + labs(title = "Austria Has Steepest Slope for Weighted Points and Price Model",
         y = "Log(Price/Points)",
         x = "Price")
```
### Discussion

Our analyses showed that the highest rated wines are from Austria, a positive relationship between price and point ratings, and also some small differences in the words used to describe highly rated and poorly rated wines.
  
Top Countries and Varieties
  
This investigation gave specific evidence against our hypothesis that Italy and France would be the countries with the highest rated wines. Instead, both Austria and Germany had on average higher point ratings for their wines than these two countries. This information was especially surprising considering Italy and Spain were the top wine producers in 2019, and Forbes rated Napa Valley as the source of the best ranked wine in the same year. Because only "wine experts" gave data for the data set used in this investigation, we think that the point system more closely resembles a niche set of wine connoisseurs than the general public. Moreover, we recognize that this list of top 5 countries may not be an accurate representation of where the best wines come from, but rather a representation of what location on average has the wines with the highest point ratings. This calculation rewards countries with one highly rated wine and disadvantages countries that have wines represented in the data set with very high point values and more very poorly rated wines. The density plots for price and points further convey Austria as a source of better wine. Austria clearly has a larger proportion of higher rated wines than the other top 5 countries yet at similar price ranges. Also, Austria's wines were generally cheaper than the other countries. The density plots for top varieties showed that the Gewürztraminer wine variety had a more evenly distributed range of wines scores and prices, but a higher wine score on average. This might mean that while choosing a Gewürztraminer could give you a very highly rated wine, you could also have a lower rated wine. Whereas the less evenly distributed Grüner Veltliner variety primarily has wines with scores of at least 90.
  
Relationship Between Price and Points  

The linear models for predicted price both give evidence for a positive strong relationship between price and points. The linear model that predicted the number of points a wine would receive with a price factor had a p value of 3.77e-311 for the price factor. At an alpha level of 0.05, this gives strong evidence against a null hypothesis that there is no relationship between price and points. The linear model with top countries and top variety factors gave p values of 5.56e-21 and 1.63e-56, respectively. At an alpha level of 0.05, this gives strong evidence against a null hypothesis that there is no relationship between being in the top variety or country and the point value. This means that when choosing a wine to maximize points awarded by wine connoisseurs, it makes the most sense to choose a wine from one of these top countries and varieties. It should be noted that the data for the linear model was not normally distributed. This makes analysis using a linear model less effective.
  
Text Analysis
  
In our analysis of the text description, we found that tannins and lemon both fall near the bottom of the graph for both groups, but that the words acidity and ripe fall in the top 4 for both graphs as well. We hypothesize this is the case because these are things that are present in most wines, regardless of score. Lemon is a bit of an outlier in the sense that it is not a flavor that is commonly thought of when considering wines. This could be indicative that our sample size may not be as representative as we initially believed. Where we begin to see differences however, are right at the top of the graphs. We see that the word cherry is very commonly used in the descriptions of the top 5 wines. We also see dry and red rounding out the top 5. On the other graph, we notice that black, plum, and white are very common descriptors as well as apple and berry rounding out their top 10.

From this, we can hypothesize that a highly rated wine is more likely to be a dry red with hints of cherry. While a lowly rated wine is likely to be a fruity white wine, or potentially a very dark red (where we imagine the black descriptor comes from) again with fruity hints outside of cherries. When comparing words used to describe cheap wines and expensive wines, we found that words used to describe expensive wines were also also found in poorly rated wines. On the other hand, words used to describe cheap wines were also found in highly rated wines. This indicates to us that when selecting a wine, you should still consider price, but price is not the only factor that determines good wines. You should also take into account country, variety, and previous wine ratings.
  
In order to test these hypotheses in a future analysis we could count these words and perform a CLT based test to determine if the differences in probabilities of words in the top 5 wines or worst 5 wines are statistically different. Furthermore, in the future it would be interesting to assign either a positive or negative value to words used in the description of wines and perform a statistical test to quantify whether there is a significant difference in positive or negative words used to describe different categories of wine. We would be also interested in combining this wine rating data with data on wine purchases to compare how and if consumer decisions align with the trends we found in our data investigation. 
  
### References

[1] “Where Did Wine Come From? The True Origin of Wine.” Wine Folly, 19 Oct. 2020, winefolly.com/deep-dive/where-did-wine-come-from/. 

[2] Conway, Published by Jan, and May 13. “Leading Countries in Global Wine Production, 2019.” Statista, 13 May 2020, www.statista.com/statistics/240638/wine-production-in-selected-countries-and-regions/.

[3] Huen, Eustacia. “The World's 30 Best Wines In 2019.” Forbes, Forbes Magazine, 26 Mar. 2019, www.forbes.com/sites/eustaciahuen/2019/03/25/wine-3/. 

### Appendix

### Appendix A

``` {r lm_model, message = F, warning = F, echo = F}
tidy(modell)
```

### Appendix B

``` {r descriptor_plots_1, message = F, warning = F, echo = F, fig.height = 3, fig.width = 5}
ggplot(data = top_5_descriptor_counts, aes(fct_reorder(word, prob), prob)) +
    geom_col(color = "darkblue", fill = "skyblue") +
    coord_flip() + 
    theme_minimal() +
    labs(title = "Frequency Of Descriptor Words In Top 5 Wines",
         x = "Descriptor Words",
         y = "Frequency")
```

### Appendix C

```{r descriptor_plots_2, message = F, warning = F, echo = F, fig.height = 3, fig.width = 5}
ggplot(data = bottom_5_descriptor_counts, aes(fct_reorder(word, prob), prob)) +
    geom_col(color = "darkblue", fill = "skyblue") +
    coord_flip() + 
    theme_minimal() +
    labs(title = "Frequency Of Descriptor Words In Bottom 5 Wines",
         x = "Descriptor Words",
         y = "Frequency")
```

### Appendix D

``` {r cheap_vs_expensive_descriptor_plots_1, message = F, warning = F, echo = F, fig.height = 3, fig.width = 5}
ggplot(data = expensive_wine_word_counts, aes(fct_reorder(word, prob), prob)) +
    geom_col(color = "darkblue", fill = "skyblue") +
    coord_flip() + 
    theme_minimal() +
    labs(title = "Frequency Of Descriptor Words In Expensive Wines",
         x = "Descriptor Words",
         y = "Frequency")
```

### Appendix E

```{r cheap_vs_expensive_descriptor_plots_2, message = F, warning = F, echo = F, fig.height = 3, fig.width = 5}
ggplot(data = cheap_wine_word_counts, aes(fct_reorder(word, prob), prob)) +
    geom_col(color = "darkblue", fill = "skyblue") +
    coord_flip() + 
    theme_minimal() +
    labs(title = "Frequency Of Descriptor Words In Cheap Wines",
         x = "Descriptor Words",
         y = "Frequency")
```

In working on our text and sentiment analysis, we quickly realized that we had to do some filtering beyond just a standard stop word anti join. To do this, we would run our code to retrieve the top 20 most common words that appeared in the descriptions for our different categories, and then analyze them to see if they all made sense. After repeating this many times, we felt that we had a representative sample of descriptors that were significant. Some of them were removed based off of the specific filter. For example, if we were filtering for Pinot Noirs, we didn't need to see the word Pinot in our top 20 descriptors. Additionally, we chose words like generous that didn't seem to tell us much and other words like wine and flavors that can reasonably be expected to be present in every description. There was certainly a bit of arbitrary choice involved here, but we felt all of the words taken out were not relevant to the comparisons we were making. Below you will find a list of the words we removed. 
wine, flavors, palate, drink, aromas, offers, finish, notes, long, generous, hints, nose, fresh, fruit, full, character, ready, 100,  merlot, texture, end, medium, bodied, malbec, portuguese, chardonnay, blanc, viognier, note, show, vineyard, style, shows, make, pinot, sauvignon, body, bottling, alongside, dense, dried, concentrated, years, vineyard, structure, age, fruits